### 2014-07-01 tex/main-body-text.tex
minor edits to correct some merge edits that I reverted

\subsection*{Results} 
Run times for both programs were relatively short, albeit non-trivial. All runs of {\sc flock} 
completed in 1133 minutes. Each of the six groups of runs averaged 188.8 minutes.
All runs of {\sc structure} were completed in 
486 minutes and averaged 80.8 minutes to complete each of the six groups of runs.
The processing time of each algorithm increased with as the number or 
putative clusters increases. Increasing
$K$ from of 2 to 6 increased the run time for {\sc flock} by a factor of 2.4, while the run time 
for {\sc structure} increased by a factor of only 1.6.

{\sc flock} and {\sc structure} provide similar results in 
terms of how individuals are allocated among runs at low values of $K$, 
while, at larger values, {\sc flock} often found, in addition to the solution identified by {\sc structure}, 
multiple other solutions. For all six groups 
of runs for \textit{k} = 2 - 4, {\sc flock} resulted in nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from results obtain from 
{\sc structure} (Fig 1). Of the 'best runs' for the six groups for \textit{k} of 2, two  
runs yielded identical clustering (same mean LLOD score), all other runs 
differed by at most the allocation of 13 individuals. As 
\textit{k} increases so do the number of solutions
that {\sc flock} finds (Fig 1). For all groups of runs for $K$ $\geq 2$, no plateaus were observed - all intial 
allocations resulted in solutions that differed. 
It is unclear in these cases what constitutes the 'best run' as all plateau lengths are 
equal to one. Many of these solutions are, however, suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal},
although less reliably so in the case of {\sc flock}.

@@

\begin{figure*}
\begin{center}
	 % NOTE. Eric made Flock-Fig1.jpg as a Preview because Flock-Fig1.pdf
	 % ate up too many resources while editing the document.  For final 
	 % production, it should be changed back to Flock-Fig1.pdf
    \includegraphics[width=\textwidth]{images/Figures-Pat/Flock-Fig1-GreyScale.pdf} % Flock-Fig1.jpg}  
    \caption{Plots of $q_i$ values from {\sc structure} and the normalized likelihood values 
from {\sc flock} made in the program Distruct. Each horizontal plot represents an individual run of the program {\sc structure}, or the 'best run' from a series of runs in {\sc flock}. Within each plot 
$q_i$ values from {\sc structure} and the normalized likelihood values 
from {\sc flock}  are represented by a 
colored vertical bar.  Results from 
from the 'best runs' of {\sc flock} showed similar geographic differentiation to 
\citet{Garzaetal_norcal}.}
    \label{Fig.1}
\end{center}
\end{figure*}

@@

One of the major claimed advantages of {\sc flock} over MCMC methods for solving the 
K-partition problem is that, '[t]he very short processing times for each run of {\sc flock} allows for
 comparing partitions from many runs of each \textit{k}'' \citep[][p.~735]{Duc&Tur2012}.
While the authors observed improved process time in their 
comparisions we did not observe the same advantage in our analysis. In their comparison, the 
run parameters for {\sc flock} were 50 runs and 20 iterations for each \textit{k} = 1 to K+4. 
These process times were compared to the admixture model with correlated allele 
frequencies in {\sc structure} with ten iterations of a 50,000 sweep burn-in followed 
by 200,000 sweep sample from the posterior of \textit{k} from 1 to K+3. 
It seems reasonable, for each \textit{k}, to compare one iteration of {\sc structure} 
to one iteration of {\sc flock} with 50 different starting allocations that are reallocated 20 times 
as both evaluate the partition space once. Process speed advantages also may only been observed 
with low sample sizes. The authors evaluated simulated data sets with sample sizes of N = 60, 120, 
and 240.

>>>>

\subsection*{Results} 
Run times for both programs were relatively short, albeit non-trivial. All runs of {\sc flock} 
completed in 1133 minutes. Each of the six groups of runs averaged 188.8 minutes.
All runs of {\sc structure} were completed in 
486 minutes and averaged 80.8 minutes to complete each of the six groups of runs.
The processing time of each algorithm increased as the number or 
putative clusters increases. Increasing
$K$ from of 2 to 6 increased the run time for {\sc flock} by a factor of 2.4, while the run time 
for {\sc structure} increased by a factor of 1.6.

{\sc flock} and {\sc structure} provide similar results in 
terms of how individuals are allocated among runs at low values of $K$, 
while at larger values, {\sc flock} often found, in addition to the solution identified by {\sc structure}, 
multiple other solutions. For all six groups 
of runs for \textit{k} = 2 - 4, {\sc flock} resulted in nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from results obtain from 
{\sc structure} (Fig 1). Of the 'best runs' for the six groups for $K$ = 2, two  
runs yielded identical clustering (same mean LLOD score) while all other runs 
differed by at most the allocation of 13 individuals. As 
\textit{k} increases so do the number of solutions
that {\sc flock} found (Fig 1). For all groups of runs for $K$ $\geq 2$, no plateaus were observed - all intial 
allocations resulted in solutions that differed. 
It is unclear in these cases what constitutes the 'best run' as all plateau lengths are 
equal to one. Many of these solutions are, however, suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal},
although less reliably so in the case of {\sc flock}.

@@

\begin{figure*}
\begin{center}
	 % NOTE. Eric made Flock-Fig1.jpg as a Preview because Flock-Fig1.pdf
	 % ate up too many resources while editing the document.  For final 
	 % production, it should be changed back to Flock-Fig1.pdf
    \includegraphics[width=\textwidth]{images/Figures-Pat/Flock-Fig1-GreyScale.pdf} % Flock-Fig1.jpg}  
    \caption{Plots of $q_i$ values from {\sc structure} and the normalized likelihood values 
from {\sc flock} made in the program Distruct. Each horizontal plot represents an individual run of the program {\sc structure}, or the 'best run' from a series of runs in {\sc flock}. Within each plot 
$q_i$ values from {\sc structure} and the normalized likelihood values 
from {\sc flock}  are represented by a 
colored vertical bar.  Results from 
from the 'best runs' of {\sc flock} showed similar geographic differentiation to 
\citet{Garzaetal_norcal}.}
    \label{fig:qplots}
\end{center}
\end{figure*}

@@

One of the major claimed advantages of {\sc flock} over MCMC methods for solving the 
K-partition problem is that, 'The very short processing times for each run of {\sc flock} allows for
 comparing partitions from many runs of each \textit{k}'' \citep[][p.~735]{Duc&Tur2012}.
While the authors observed improved process time in their 
comparisions we did not observe the same advantage in our analysis. In their comparison, the 
run parameters for {\sc flock} were 50 runs and 20 iterations for each \textit{k} = 1 to K+4. 
These process times were compared to the admixture model with correlated allele 
frequencies in {\sc structure} with ten iterations of a 50,000 sweep burn-in followed 
by 200,000 sweep sample from the posterior of \textit{k} from 1 to K+3. 
It seems reasonable, for each \textit{k}, to compare one iteration of {\sc structure} 
to one iteration of {\sc flock} with 50 different starting allocations that are reallocated 20 times 
as both evaluate the partition space once. Process speed advantages also may only been observed 
with low sample sizes. The authors evaluated simulated data sets with sample sizes of N = 60, 120, 
and 240.
